DRAFT: Harmonized and trait aggregation paper

### 2020-10-21 Paper/Draft_harmonization_paper.tex
21.10: Started results simulation

To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we simulated three different taxonomic hierarchies. 
Sim1) A family with an equal number of genera and species (5 genera each with 5 species respectively).
Sim2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively). 
Sim3) A family where all genera have a different number of species (8, 2, 7, 3, 5).
Every simulated taxonomic hierarchy was assigned a hypothetical grouping feature with 3 traits. The affinities for each trait were sampled from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviation (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability. The truncated normal distribution was bound to 0 and 1. The traits were normalized so that they sum up to one for each species, similar to the data processing of the trait databases. 100 Simulations for each standard deviation were carried out. Hence, 
500 simulations were run for each simulation scenario (in total 1500). All trait aggregation methods were applied to each simulated dataset and the results were compared.

>>>>

To examine the influence of the taxonomic hierarchy and the trait variability on the outcome of the different trait aggregation methods we simulated three different taxonomic hierarchies. 
1) A family with an equal number of genera and species (5 genera each with 5 species respectively) 
% denoted as \textit{equal scenario}.
2) A family where one genus has a much larger number of species than the other 4 genera (1 genus with 13 species, 4 genera with 3 species respectively). 
3) A family where all genera have a different number of species (8, 2, 7, 3, 5).
Every simulated taxonomic hierarchy was assigned a hypothetical grouping feature with 3 traits. The affinities for each trait were sampled from a truncated normal distribution with a mean value of 0.5 and 5 levels of standard deviation (0.2, 0.4, 0.6, 0.8, and 1) respectively to simulate different levels of trait variability. The truncated normal distribution was bound to 0 and 1. The traits were normalized so that they sum up to one for each species, similar to the data processing of the trait databases. 100 Simulations for each standard deviation were carried out. Hence, 500 simulations were run for each simulation scenario (in total 1500). All trait aggregation methods were applied to each simulated dataset and the results were compared.
